Learning Features and Abstract Actions for Computing Generalized Plans

### 2018-11-14 doc/camera-ready/paper.tex
Last minute changes

A \emph{feature} $f$ for a class $\Q$ of problems represents a function $\phi_f$
that takes an instance $P$ from $\Q$ and a state $s$ reachable in $P$, and results
in a value $\phi_f(s)$.
A feature is \emph{boolean} if it results in boolean values, and \emph{numeric}
if it results in numerical values. %, that we assume to be a non-negative integer.
For example, $H$ and $n(x)$ represent two features in the Blocksworld:
the first is a boolean feature that tracks whether the gripper is empty, while
the second is numerical and tracks the number of blocks above $x$.

>>>>

A \emph{feature} $f$ for a class $\Q$ of problems represents a function $\phi_f$
that takes an instance $P$ from $\Q$ and a state $s$ reachable in $P$, and results
in a value denoted as $\phi_f(s)$.
A feature is \emph{boolean} if it results in boolean values, and \emph{numeric}
if it results in numerical values. %, that we assume to be a non-negative integer.
For example, $H$ and $n(x)$ represent two features in Blocksworld:
$H$ is a boolean feature that tracks whether the gripper is empty, while
$n(x)$ is numerical and tracks the number of blocks above $x$.
